Playing against Nature: causal discovery for decision making under uncertainty

### 2018-05-18 Segundo_Semestre/CausalML_Workshop/Paper_long_version.tex
por qué matrices en caso3

We require that this measure satisfies the Markov Causal Condition, Causal Minimality and Causal Faithfulness as stated in \cite{spirtes2000causation}. The relation between $\mathbb{P}$ and $P_{\mathcal{G}}$ is given by the Manipulation Theorem of \cite{spirtes2000causation} and the Do-Calculus rules from \cite{pearl2009causality}.

@@

Since she knows the graph structure, she can explicitly find a non interventional expression for the interventional distribution and update her beliefs about this unknown quantities. If the decision maker were not allowed to know, at the end of each round, the play of the Nature then this will have to be estimated as a hidden variable using, for example, the EM algorithm but meanwhile we are assuming that this information is available at the end of each round.

@@

\subsection{The model is not known}
The causal model were unknown, the decision maker will have to deal with the problem using only any previous knowledge and his own intuitions. The set of any previous knowledge and considerations will be known as \textit{beliefs}, which will take the form of a probability distributions over causal models.

For this case we consider two sub-cases depending on the maximum number of variables in the causal model are known or not.

>>>>

We require that this measure satisfies the Markov Causal Condition, Causal Minimality and Causal Faithfulness as stated in \cite{spirtes2000causation}. The relation between $\mathbb{P}$ and $P_{\mathcal{G}}$ is given by the Manipulation Theorem of \cite{spirtes2000causation} and the Do-Calculus rules from \cite{pearl2009causality}. We also require that the condition known as Causal Sufficiency is satisfied by the model, which means there are not any causes lying \textit{outside} of the model.

@@

Notice that the base game is an extensive game with imperfect information since the decision maker makes a choice without knowing the play made by Nature, which is the asigning a disease to the patient, and then assigning the outcome for the patient after the medic has chosen a treatment.

Since she knows the graph structure, she can explicitly find a non interventional expression for the interventional distribution and update her beliefs about this unknown quantities. If the decision maker were not allowed to know, at the end of each round, the play of the Nature then this will have to be estimated as a hidden variable using, for example, the EM algorithm \cite{dempster1977maximum} but meanwhile we are assuming that this information is available at the end of each round.

@@

\subsection{The model is not known}
The causal model were fully unknown, the decision maker will have to deal with the problem using only any previous knowledge and his own intuitions. Again, consider the set of any previous knowledge and considerations will as \textit{beliefs} about the uncertainties in the environment, which will take the form of a probability distributions over causal models.

For this third case, we make an extra assumption: the maximum number of variables in the model is known to the decision maker. This allow to consider only distributions of fixed dimension. In this case we will consider distributions over matrixes of fixed size rather than vectors as in the previous case.
